

\section{Ladder Lottery Realization}

In \emph{Ladder Lottery Realization}~\cite{A3}, written by Horiyama, Uno, Wasa and Yamanaka, the authors provide 
a rather interesting puzzle in regards to ladder lotteries. The puzzle 
is known as the Ladder Lottery Realization Problem. In order to understand
the problem, one must know what a \emph{multi-set} is. A \emph{multi-set}
is a set in which an element may appear more than once. The exponent 
above the element indicates the number of times it appears in the set.
For example, given the following multi-set, $\{3^{2}, 2^{4}, 5^{1}\}$ 
the element $3$ appears twice in the set, the element $2$ appears four times
in the set and the element $5$ appears once in the set.
The Ladder Lottery Realization puzzle asks, given an arbitrary starting permutation, $\pi$, 
and a multi-set of bars, 
is there a ladder lottery for $\pi$
that uses every bar in the multi-set the number 
of times it appears in the  multi-set. 
For an example of an affirmative solution to the Ladder Lottery Realization problem, see Figure~\ref{fig:ladder realization}.

\begin{figure}[!htp]
    \begin{center}
        \begin{tikzpicture}
            \draw (0, 0) to (0, 6);
                \node at(0, -0.3){1};
                \node at(0, 6.3){4};
            \draw(2, 0) to (2, 6);
                \node at(2, -0.3){2};
                \node at(2, 6.3){1};
            \draw(4, 0) to (4, 6);
                \node at(4, 6.3){5};
                \node at(4, -0.3){3};
            \draw(6, 0) to (6, 6);
                \node at(6, 6.3){3};
                \node at(6, -0.3){4};
            \draw(8, 0) to (8, 6);
                \node at(8, 6.3){2};
                \node at(8, -0.3){5};

            %%draw the bars
                \node at(1, 6){(4,1)};
                    \draw(0, 5.75) to (2, 5.75);
            \draw(0, 5.25) to (2, 5.25);
                \node at(1, 5.55){(4,1)};
            \draw(0, 4.75) to (2, 4.75);
                \node at(1, 5){(4,1)};

            \draw(4, 5.75) to (6, 5.75);
                \node at(5, 6){(5,3)};
            \draw(4, 5.25) to (6, 5.25);
                \node at(5, 5.55){(5,3)};
            \draw(4, 4.75) to (6, 4.75);
                \node at(5, 5){(5,3)};

            \draw(2, 4.25) to (4, 4.25);
                \node at (3, 4.55){(4,3)};
            \draw(2, 3.75) to (4, 3.75);
                \node at (3, 4){(4,3)};
            \draw(2, 3.25) to (4, 3.25);
                \node at (3, 3.5){(4,3)};
            
            \draw(2, 1.5) to (4, 1.5);
                \node at(3, 1.8){(3,2)};
            
            \draw(4, 2.8) to (6, 2.8);
                \node at (5, 3.1){(4,2)};
            \draw(6, 4.25) to (8, 4.25);
                \node at (7, 4.55){(5,2)};
            
            \draw(6, 2.25) to (8, 2.25);
                \node at (7,2.75){(5,4)};
            
            \draw(6, 1.75) to (8, 1.75);
                \node at (7, 2){(5,4)};
            
        \end{tikzpicture}
    \end{center}
      


    \caption{An affirmative solution to the Ladder Lottery Realization Problem given a starting permutation $(4,1,5,3,2)$ and the multi set of bars $\{(3,2)^{1},(4,1)^{3}, (4,2)^{1},(4,3)^{3},(5,2)^{1},(5,3)^{3},(5,4)^{2}\}$}
    \label{fig:ladder realization}
\end{figure}
\pagebreak
The authors prove that the Ladder Lottery Realization problem in NP-Hard
by reducing the Ladder Lottery Realization to the One-In-Three 3SAT problem, 
which has already been proven to be NP-Hard.
The authors note that there are two cases in which the ladder lottery
realization problem can be solved in polynomial time. These cases 
include the following. First, if every bar in the multi-set appears
exactly once and every bar corresponds to an inversion, 
then an affirmative solution to the Ladder Lottery Realization 
instance can be achieved in polynomial time. 
Second, if there is an inversion in the permutation and its bar appears in the multi-set an even 
number of times, then a negative solution to
the Ladder Lottery Realization instance
can be achieved in polynomial time. This is because the elements that cross the bar will 
be uninverted when then be inverted again. Therefore $\pi$ will not be sorted by the ladder.\par