



%----------------  INTRODUCTION with THESIS STATEMENT ----------------------
\chapter{Introduction}
\label{chapter:intro}
\input{intro}


\section{Thesis Statement}
    This thesis provides three full, or partial, solutions to three problems related 
    to ladder-lotteries. The first of these problems is the so called counting problem, 
    which asks, how many ladders are in $OptL\{\pi\}$? This thesis provides 
    a formula for the exact number of ladders in $OptL\{\pi\}$, for certain 
    cases of $\pi$ as well as a general recurrence relation for $OptL\{\pi\}$
    when $\pi$ is the decending permutation. The second problem is the so called canonical ladder listing problem. 
    This problem asks, given all permutations of size $N$, is there an algorithm 
    to list a canonical ladder from each permutation's $OptL\{\pi\}$? In other words, 
    is there an easy way to transition from one permutation's canonical ladder to the next 
    permutation's canonical ladder until all permutations of size $N$ have had their canonical 
    ladder generated? This thesis provides two such algorithms.The third problem is the so called minimum height 
    problem which asks, given all the ladders in $Optl\{\pi\}$, which ladder(s) are 
    the shortest, that is to say which ladders have the smallest height? Furthermore, given some arbitrary $\pi$, 
    is there a way to create a ladder for $\pi$ with minimal height? This thesis 
    provides an upper and lower bound for the minimal height of ladders along with a heuristic algorithm 
    for creating a ladder with minimal height.
   
\section{Overview of Thesis}  

This thesis is broken down into several sections. Firstly, an introuduction to Amidakuji, 
and how they pertain to computer science will be presented. This will be followed by a literature 
review of ladder lotteries in which discussions of solved problems will be 
provided, along with the commonalities between ladder lotteries and 
other mathematical objects. Following the literature review, three chapters pertaining to the three problems will be 
provided. In each of these three chapters there is an introduction to the problem, a methodology section, a results 
section and a conclusion section. The introduction section introduces the problem to the reader, providing the necessary 
definitions and concepts. The methodology sections contain the algorithms and formulas used to solve the respective problems. 
Following the methodology sections, the results generated by the algorithms and formulas will be presented.
In the results sections there will be proofs and formulas for certain propositions made in regards to the respective problems. 
Following the results section, an analysis of the results will be presented along with a summary  of future pertaining to the problem 
will be provided. In this section,
the failures and successes of this research will be analyzed. There will also be commentary on 
open (unsolved) problems related to ladder lotteries and a 
discussion of how research on ladder lotteries could be used in other fields.
Finally, a conlcusion that summarizes the thesis will be provided.

%----------------  BACKGROUND and LITERATURE REVIEW ----------------------
\chapter{Background and Literature Review}
\label{chapter:background}
\input{background} 


\chapter{Literature Review}
\input{LitReview/LiteratureReview}

\chapter{The Counting Problem}
\label{chapter:countingProblem}
---Will Complete This Chapter Later---

%----------------  METHODOLOGY and IMPLEMENTATION ----------------------
\chapter{The Listing Problem}  
\label{chapter:listingproblem}
\input{GrayCode/Intro}
\input{GrayCode/Procedure}
\input{GrayCode/Results}
\input{GrayCode/Analysis}

\chapter{The Minimum Height Problem}
\label{chapter:minheightproblem}
\input{MinHeight/Intro}
\input{MinHeight/Procedure}



%----------------  EVALUATION or ANALYSIS ------------------------------------------
\chapter{Evaluation}  
\label{chapter:evaluation}


%----------------  SUMMARY AND FUTURE WORK -----------------------------------

\chapter{Summary and Future Work}
\label{chapter:summary}

Conclude your thesis with a re-cap of your major results and contributions.  Then outline directions for further research and remaining open problems.