%--------------------------------------------------------------------------------------------------------------------------
%  YOU MUST PUT THE FILES "gthesis.cls" and  "gct11.clo" IN SAME DIRECTORY
%
%  The content of your thesis goes in "body.tex"
%  Bibtex file in "mybib.bib"
%  If there is an appendix place it in "appendix.tex"
%---------------------------------------------------------------------------------------------------------------------------

\documentclass[11pt,dvipsnames]{gthesis}



%---- ADD PACKAGES ------
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{graphics}
\usepackage{color}
\usepackage{url}
\usepackage{lineno}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage[absolute,overlay]{textpos}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{subcaption}
\usepackage{titlesec}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{longtable}
\usepackage{url}


%\usepackage{algorithm2e}
%\SetAlFnt{\small}
%%\SetAlCapFnt{\large}
%\SetAlCapNameFnt{\large}
%%\usepackage{algorithmic}

%%\usepackage[dvipsnames]{xcolor}

\usepackage{fancyvrb}
\usepackage{listings}



\definecolor{verbgray}{gray}{0.9}


\lstnewenvironment{code}{%
  \lstset{backgroundcolor=\color{verbgray},
  frame=single,
  language=C,
  framerule=0pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{blue}\textit,
  keywordstyle=\color{black}\bf,
  numbers=none,
  keepspaces=true,
  columns=fullflexible}}{}

\newcounter{appendixNum}
% redefine \VerbatimInput
\RecustomVerbatimCommand{\VerbatimInput}{VerbatimInput}%
{fontsize=\footnotesize,
 %
 frame=lines,  % top and bottom rule only
 framesep=2em, % separation between frame and text
%% rulecolor=\color{Gray},
 %
 label=\fbox{MinLadders.txt},
 labelposition=topline,
 %
 commandchars=\|\(\), % escape character and argument delimiters for
                      % commands within the verbatimX
 commentchar=*        % comment character
}

% \RecustomVerbatimCommand{\VerbatimInputTwo}{VerbatimInput}
% {
%   fontsize=\footnotesize,
%   frame=lines,  % top and bottom rule only
%  framesep=2em, % separation between frame and text
% %% rulecolor=\color{Gray},
%  %
%  label=\fbox{MinLaddersPrint.txt},
%  labelposition=topline,
%  %
%  commandchars=\|\(\), % escape character and argument delimiters for
%                       % commands within the verbatim
%  commentchar=*        % comment character
% }

\usetikzlibrary{calc,trees,positioning,arrows,fit,shapes,calc}


%Set the depth level to 4
\setcounter{secnumdepth}{4}

%%set the paragraph to subsubsubsection
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}



%%for images
\usepackage{caption} % for \captionof



%--- ADD YOUR MACROS ------
\newtheorem{theorem}{Theorem}[section]          % Numbers theorems bysection.
\newtheorem{proposition}[theorem]{Proposition}  % Numbers a proposition by a theorem number.
\newtheorem{lemma}[theorem]{Lemma}             % Numbers a lemma by a theorem number.
\newtheorem{corollary}[theorem]{Corollary}        % Numbers a corollary by a theorem number.
\newtheorem{example}[theorem]{Example}         % Numbers an example by a theorem number.
\newtheorem{examples}[theorem]{Examples}     % Numbers a list of examples by a theorem number.
\newtheorem{remark}[theorem]{Remark}            % Numbers remark by a theorem number.
\newtheorem{remarks}[theorem]{Remarks}         % Numbers a list of remarks by a theorem number.
\newtheorem{conjecture}[theorem]{Conjecture}   % Numbers a conjecture by a theorem number.
\newtheorem{definition}[theorem]{Definition}       % Numbers a definition by a theorem number.

%%Envoironments
\newenvironment{proof}{{\em Proof.}}{\hspace*{\fill}$\Box$\par\vspace{4mm}}

\newcounter{casenum}
\newenvironment{caseof}{\setcounter{casenum}{1}}{\vskip.5\baselineskip}
\newcommand{\case}[2]{\vskip.5\baselineskip\par\noindent {\bfseries Case \arabic{casenum}:} #1\\#2\addtocounter{casenum}{1}}

%%tree 
\tikzset{
  treenode/.style = {shape=rectangle, rounded corners,
                     draw, align=center,
                     top color=white, bottom color=blue!20},
  root/.style     = {treenode, font=\small, bottom color=red!30},
  env/.style      = {treenode, font=\ttfamily\small},
  dummy/.style    = {circle,draw}
}

%%%COMMANDS 
\newcommand{\dividepage}{%
  \par\noindent
  \makebox[\linewidth]{\raisebox{.2\baselineskip}{\makebox[2\paperwidth]{\dotfill}}}%
  \par
}




%------------------------------------------------------------------------------------------------------------------------------------i
\begin{document}

%--- TITLE PAGE   --------------------------
\title{Amidakuji: Gray Code Algorithms and Equations for Listing Ladder Lotteries}

\author{Patrick Di Salvo}

\type{Thesis}   

\degree{Master of Science}     % Change degree/field to PHD if appropriate
\field{Computer Science}  	

%\degree{Doctor of Philosophy} 	
%\field{Computational Sciences}  


\advisorLabel{Advisor}		% set to Advisors if multiple
\advisor{Dr. Joseph Sawada}

\degreemonth{August}
\degreeyear{2021}

\maketitle

%--- ABSTRACT  --------------------------
% Recommended word limit is 150 for Masters and 350 for doctoral.
% Try to abide.



\begin{frontmatter}

\begin{abstract}
  \addcontentsline{toc}{chapter}{Abstract}

We provide a Gray code for listing ladder lotteries in which successive ladders differ by the addition/removal of a single bar or 
the relocation of a bar. Ladder lotteries are an abstract mathematical object which correspond to permutations. They are a network of vertical lines 
and horizontal bars, which induce transpositions on elements in a specific permutation when the lines cross. 
Ladder lotteries are of interest to the field of theoretical computer science because of their relationship with other 
mathematical objects such as primitive sorting networks. 
To list ladder lotteries, we define a function that calculates the location for any bar in the data structure in $O(1)$ time. We provide an $O(n^2)$ amortized 
algorithm for creating a specific ladder corresponding to a specific permutation. We provide an $O(1)$ amortized algorithm for listing 
 $n!$ canonical ladders by adding or removing a bar. Finally, we provide a Gray code for listing $n!$ ladders ordered by 
 the number of bars. 

\medskip

\small
\centering

\end{abstract}
\end{frontmatter}


%============FRONT MATTER=============================

%--- ACKNOWLEDGEMENTS  ------
\begin{frontmatter}

\begin{acknowledgements}
    \addcontentsline{toc}{chapter}{Acknowledgements}

	I would like to thank my advisor Dr. Joe Sawada, my second reader Dr. Charlie Obimbo, my non-advisory committee member Dr. Steve 
	Gismondi, the committee chair Dr. Mark Wineberg, and the graduate assistant Jennifer Hughes for their help with the completion 
	of this thesis. 
\end{acknowledgements}




%--- TABLE OF CONTENTS AND LIST OF FIGURES  ------
\tableofcontents
\listoftables
\listoffigures

\end{frontmatter}
%======================================================

%--- MAIN BODY OF THESIS  ------
\dsp
\include{body}

%--- BIBLIOGRAPHY  ------
\ssp
  \bibliographystyle{abbrv}
  \bibliography{mybib}
\dsp

%--- APPENDIX  ------

\appendix
\include{appendix}

\end{document} 
