%--------------------------------------------------------------------------------------------------------------------------
%  YOU MUST PUT THE FILES "gthesis.cls" and  "gct11.clo" IN SAME DIRECTORY
%
%  The content of your thesis goes in "body.tex"
%  Bibtex file in "mybib.bib"
%  If there is an appendix place it in "appendix.tex"
%---------------------------------------------------------------------------------------------------------------------------

\documentclass[11pt,draft]{gthesis}



%---- ADD PACKAGES ------
%\usepackage{setspace}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{graphics}
\usepackage{color}
\usepackage{url}
\usepackage{lineno}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage[absolute,overlay]{textpos}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{subcaption}
\usepackage{titlesec}
\usepackage[font=small,labelfont=bf]{caption}
%\usepackage{algorithm2e}
%\SetAlFnt{\small}
%%\SetAlCapFnt{\large}
%\SetAlCapNameFnt{\large}
%%\usepackage{algorithmic}


\usepackage[dvipsnames]{xcolor}

\usepackage{fancyvrb}

% redefine \VerbatimInput
\RecustomVerbatimCommand{\VerbatimInput}{VerbatimInput}%
{fontsize=\footnotesize,
 %
 frame=lines,  % top and bottom rule only
 framesep=2em, % separation between frame and text
%% rulecolor=\color{Gray},
 %
 label=\fbox{MinLadders.txt},
 labelposition=topline,
 %
 commandchars=\|\(\), % escape character and argument delimiters for
                      % commands within the verbatim
 commentchar=*        % comment character
}


\usetikzlibrary{calc,trees,positioning,arrows,fit,shapes,calc}


%Set the depth level to 4
\setcounter{secnumdepth}{4}

%%set the paragraph to subsubsubsection
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}



%%for images
\usepackage{caption} % for \captionof



%--- ADD YOUR MACROS ------
\newtheorem{theorem}{Theorem}[section]          % Numbers theorems bysection.
\newtheorem{proposition}[theorem]{Proposition}  % Numbers a proposition by a theorem number.
\newtheorem{lemma}[theorem]{Lemma}             % Numbers a lemma by a theorem number.
\newtheorem{corollary}[theorem]{Corollary}        % Numbers a corollary by a theorem number.
\newtheorem{example}[theorem]{Example}         % Numbers an example by a theorem number.
\newtheorem{examples}[theorem]{Examples}     % Numbers a list of examples by a theorem number.
\newtheorem{remark}[theorem]{Remark}            % Numbers remark by a theorem number.
\newtheorem{remarks}[theorem]{Remarks}         % Numbers a list of remarks by a theorem number.
\newtheorem{conjecture}[theorem]{Conjecture}   % Numbers a conjecture by a theorem number.
\newtheorem{definition}[theorem]{Definition}       % Numbers a definition by a theorem number.

%%Envoironments
\newenvironment{proof}{{\em Proof.}}{\hspace*{\fill}$\Box$\par\vspace{4mm}}

\newcounter{casenum}
\newenvironment{caseof}{\setcounter{casenum}{1}}{\vskip.5\baselineskip}
\newcommand{\case}[2]{\vskip.5\baselineskip\par\noindent {\bfseries Case \arabic{casenum}:} #1\\#2\addtocounter{casenum}{1}}

%%tree 
\tikzset{
  treenode/.style = {shape=rectangle, rounded corners,
                     draw, align=center,
                     top color=white, bottom color=blue!20},
  root/.style     = {treenode, font=\small, bottom color=red!30},
  env/.style      = {treenode, font=\ttfamily\small},
  dummy/.style    = {circle,draw}
}

%------------------------------------------------------------------------------------------------------------------------------------i
\begin{document}

%--- TITLE PAGE   --------------------------
\title{Amidakuji: Counting, Listing and Optimization Algorithms}

\author{Patrick Di Salvo}

\type{Thesis}   

\degree{MsC}     % Change degree/field to PHD if appropriate
\field{Computer Science}  	

%\degree{Doctor of Philosophy} 	
%\field{Computational Sciences}  


\advisorLabel{Advisor}		% set to Advisors if multiple
\advisor{Dr. Joseph Sawada}
\advisorS{Dr. Charlie Obimbo}	        		% if there is a co-advisor, add here

\degreemonth{December}
\degreeyear{2020}

\maketitle

%--- ABSTRACT  --------------------------
% Recommended word limit is 150 for Masters and 350 for doctoral.
% Try to abide.

\begin{abstract}

Amidakuji, or ladder-lotteries in English, are an abstract mathematical object which correspond to permutations. First written about in 2010, ladder-lotteries 
are a relatively new mathematical object. They are of interest to the field of theoretical computer science because of their similarities to other 
mathematical objects such as primitive sorting networks.
This thesis provides an overview of ladder-lotteries along with solutions to three problems pertaining to ladder-lotteries;
these problems are known as the counting problem, the listing problem and the minimal height problem. The solutions to these problems come in the form 
of novel algorithms, recurrence relations and formulas. The study of ladder-lotteries 
falls under the sub-discipline of theoretical computer science. The potential applications for ladder-lotteries is also discussed in this thesis, 
along with the similarities between ladder-lotteries and other mathematical objects.

\medskip

\small
\centering

\end{abstract}

%============FRONT MATTER=============================
\begin{frontmatter}

%--- ACKNOWLEDGEMENTS  ------

\begin{acknowledgements}
I do not know whom I should include here. I am assuming my advisor and second reader, but I am not sure.
\end{acknowledgements}


%--- TABLE OF CONTENTS AND LIST OF FIGURES  ------

\tableofcontents
\listoftables
\listoffigures

\end{frontmatter}
%======================================================

%--- MAIN BODY OF THESIS  ------
\dsp
\include{body}

%--- BIBLIOGRAPHY  ------
\ssp
  \bibliographystyle{abbrv}
  \bibliography{mybib}
\dsp

%--- APPENDIX  ------

\appendix
\include{appendix}

\end{document} 